---
title: "Module 3 Codebook — Model Evaluation and Resampling"
subtitle: "Applied Machine Learning for Marketing"
description: "Hands-on R notebook covering regression and classification metrics with yardstick, cross-validation with rsample, and fit_resamples() for trustworthy model performance estimates. Includes eight exercises."
author: "Jae Jung"
date: today
format:
  html:
    toc: true
    toc-depth: 4
    toc-expand: 1
    toc-location: right-body
    toc-title: "Contents"
    number-sections: true
    code-fold: show
    code-tools: true
    #theme: cosmo
    highlight-style: github
    df-print: paged
    embed-resources: true
execute:
  warning: false
  message: false
  freeze: true
  #error: true
---

# Learning Objectives {.unnumbered}

By the end of this notebook you will be able to:

1.  Choose appropriate regression and classification metrics with `yardstick`
2.  Read and interpret a confusion matrix, sensitivity, specificity, and ROC/AUC
3.  Explain *why* evaluating a model on its own training data is overly optimistic (resubstitution)
4.  Build cross-validation folds with `vfold_cv()` and other resampling schemes with `rsample`
5.  Use `fit_resamples()` to get a trustworthy estimate of model performance
6.  Connect resampled performance back to the metrics from Section 1

> **Textbook reference:** *Tidy Modeling with R* (TMWR), Chapters 9 & 10 (<https://www.tmwr.org/performance>, <https://www.tmwr.org/resampling>)

------------------------------------------------------------------------

# Setup

```{r setup}
library(tidymodels) # umbrella: rsample, recipes, parsnip, workflows, yardstick
library(tidyverse)
library(gt) # pretty tables
library(patchwork) # combine plots

tidymodels_prefer() # resolve function-name conflicts
set.seed(2026)
```

------------------------------------------------------------------------

# The Marketing Dataset

We return to our synthetic **direct-mail** dataset from Week 2. Each row is one prospect; the outcome is whether they **responded** (bought).

```{r load-data}
# ── Synthetic direct-mail dataset (same generator as Week 2 / Week 7) ─────────
set.seed(123)
n <- 3000

mail_data <- tibble(
  customer_id = paste0("C", str_pad(1:n, 5, pad = "0")),
  age = round(rnorm(n, mean = 45, sd = 12)),
  income = round(rlnorm(n, meanlog = 10.8, sdlog = 0.6)), # right-skewed
  recency_days = round(rexp(n, rate = 1 / 60)), # days since last purchase
  freq_12mo = rpois(n, lambda = 3), # purchases in 12 months
  avg_order_amt = round(rlnorm(n, meanlog = 4.2, sdlog = 0.5), 2),
  channel = sample(
    c("email", "direct_mail", "digital"),
    n,
    replace = TRUE,
    prob = c(0.5, 0.3, 0.2)
  ),
  region = sample(
    c("West", "South", "Midwest", "Northeast"),
    n,
    replace = TRUE
  ),
  loyalty_tier = factor(
    sample(
      c("Bronze", "Silver", "Gold", "Platinum"),
      n,
      replace = TRUE,
      prob = c(0.4, 0.3, 0.2, 0.1)
    ),
    levels = c("Bronze", "Silver", "Gold", "Platinum")
  ),
  responded = rbinom(
    n,
    1,
    prob = plogis(
      -3 +
        0.02 * (age - 45) +
        0.3 * log(income / 50000) +
        0.1 * freq_12mo -
        0.005 * recency_days
    )
  )
) |>
  mutate(
    income = if_else(runif(n) < 0.08, NA_real_, income),
    avg_order_amt = if_else(runif(n) < 0.05, NA_real_, avg_order_amt),
    responded = factor(responded, levels = c(1, 0), labels = c("yes", "no"))
  )
# introduce ~8 % missingness in income and avg_order_amt

glimpse(mail_data)
```

We also derive a **continuous** target — `order_value_next` — so we have a realistic stand-in for regression metrics in Section 1. Think of this as "expected next-order revenue," something a marketer might forecast for budget planning.

```{r derive-regression-target}
mail_data <- mail_data |>
  mutate(
    order_value_next = round(
      pmax(
        0,
        15 +
          0.0006 * coalesce(income, median(income, na.rm = TRUE)) +
          4 * freq_12mo -
          0.05 * recency_days +
          rnorm(n, 0, 20)
      ),
      2
    )
  )

mail_data |> select(customer_id, order_value_next) |> head()
```

::: callout-note
**Marketing context.** `responded` (yes/no) is our **classification** target — will this prospect respond to the next campaign? `order_value_next` is our **regression** target — how much will they spend on their next order? Both are common marketing prediction tasks, and TMWR Chapter 9 covers metrics for each.
:::

------------------------------------------------------------------------

# Train/Test Split and a Reference Model

Before we can evaluate anything, we need a fitted model. We reuse the same split-then-recipe workflow from Week 2.

```{r split}
set.seed(617)
mail_split <- initial_split(mail_data, prop = 0.80, strata = responded)
mail_train <- training(mail_split)
mail_test <- testing(mail_split)

cat("Training rows:", nrow(mail_train), "\n")
cat("Test rows    :", nrow(mail_test), "\n")
```

```{r recipe-model}
mail_rec <- recipe(
  responded ~ age +
    income +
    recency_days +
    freq_12mo +
    avg_order_amt +
    channel +
    region +
    loyalty_tier,
  data = mail_train
) |>
  step_impute_median(all_numeric_predictors()) |>
  step_log(income, avg_order_amt, recency_days, base = 10, offset = 1) |>
  step_normalize(all_numeric_predictors()) |>
  step_dummy(all_nominal_predictors()) |>
  step_zv(all_predictors())

lr_spec <- logistic_reg(penalty = 0.01, mixture = 1) |> # Lasso
  set_engine("glmnet") |>
  set_mode("classification")

mail_wf <- workflow() |>
  add_recipe(mail_rec) |>
  add_model(lr_spec)

mail_fit <- fit(mail_wf, data = mail_train)
```

```{r predict-test}
test_preds <- augment(mail_fit, new_data = mail_test)
test_preds |>
  select(customer_id, responded, .pred_class, .pred_yes, .pred_no) |>
  head()
```

------------------------------------------------------------------------

# **Part 1** — Judging Model Effectiveness (TMWR Ch. 9)

-   A fitted model is only useful if we can say, in concrete numeric terms, *how good* its predictions are. 

-   `yardstick` is the tidymodels package for this — every metric function takes `truth` and an `estimate`/probability column and returns a tidy one-row tibble.

## Why Metrics, Not Just "It Fit"

::: callout-important
**There is no single "best" metric.** The right metric depends on the business question. For a churn model, missing a true churner (low **sensitivity**) might be far more costly than flagging a loyal customer by mistake (low **specificity**). Always pick metrics that match the marketing decision the model supports.
:::

## Regression Metrics

We don't have a regression *model* yet in this notebook, so we'll fit one quickly — predicting `order_value_next` from a few predictors — purely to demonstrate the metrics.

```{r reg-model}
reg_spec <- linear_reg() |>
  set_engine("lm")

reg_rec <- recipe(
  order_value_next ~ income + freq_12mo + recency_days,
  data = mail_train
) |>
  step_impute_median(all_numeric_predictors()) |>
  step_normalize(all_numeric_predictors())

reg_wf <- workflow() |> add_recipe(reg_rec) |> add_model(reg_spec)
reg_fit <- fit(reg_wf, data = mail_train)

reg_preds <- augment(reg_fit, new_data = mail_test)
reg_preds |> select(customer_id, order_value_next, .pred, .resid) |> head()
```

```{r reg-metrics}
reg_metrics <- metric_set(rmse, rsq, mae)

reg_preds |>
  reg_metrics(truth = order_value_next, estimate = .pred)
```

### **RMSE** (root mean squared error): 

Average prediction error, in the *original units* (dollars here). Penalizes large errors more heavily because errors are squared before averaging.

::: {.callout-note title="RMSE Formula"}
$$
RMSE = \sqrt{\frac{1}{n}\sum_{i=1}^{n}(y_i - \hat{y}_i)^2}
$$

- Where 

  - $n$ is the number of observations, 
  - $y_i$ is the actual value, and 
  - $\hat{y}_i$ is the predicted value. 
  - $(y_i - \hat{y}_i)$ = the residual (prediction error) for observation $i$

- RMSE is in the **same units as the outcome variable** — dollars, in our case — making it directly interpretable.
:::

### **R² (rsq)**:

- Proportion of variance in the outcome explained by the model. 

- Ranges roughly 0–1; higher is better. 

- Useful for communicating "how much of next-order value our model explains" to stakeholders.

::: {.callout-note title="R-Squared formula"}
$$
R^2 = 1 - \frac{\sum_{i=1}^{n}(y_i - \hat{y}_i)^2}{\sum_{i=1}^{n}(y_i - \bar{y})^2}
$$

Where:

- $y_i$ = actual value for observation $i$
- $\hat{y}_i$ = predicted value for observation $i$
- $\bar{y}$ = mean of all actual values
- $\sum_{i=1}^{n}(y_i - \hat{y}_i)^2$ = total unexplained variation (residual sum of squares)
- $\sum_{i=1}^{n}(y_i - \bar{y})^2$ = total variation in the outcome (total sum of squares)
:::

### **MAE** (mean absolute error): 

- Average absolute error, less sensitive to outliers than RMSE. 

- If a few extreme spenders are skewing RMSE, compare it against MAE.

::: {.callout-note title="MAE Formula"}
$$
MAE = \frac{1}{n}\sum_{i=1}^{n}|y_i - \hat{y}_i|
$$

Where:

- $n$ = number of observations
- $y_i$ = actual value for observation $i$
- $\hat{y}_i$ = predicted value for observation $i$
- $|y_i - \hat{y}_i|$ = absolute prediction error for observation $i$
:::

```{r reg-plot}
#| fig-height: 4.5
#| fig-width: 6
ggplot(reg_preds, aes(x = order_value_next, y = .pred)) +
  geom_point(alpha = 0.3, color = "#2E5266") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "tomato") +
  labs(
    title = "Predicted vs. Actual Next-Order Value",
    subtitle = "Dashed line = perfect prediction",
    x = "Actual order value ($)",
    y = "Predicted order value ($)"
  ) +
  theme_minimal(base_size = 12)
```

## Binary Classification Metrics

Back to our `responded` (yes/no) model. The starting point for classification metrics is the **confusion matrix**: a 2×2 table of predicted vs. actual class.

```{r conf-mat}
conf_mat(test_preds, truth = responded, estimate = .pred_class)
```

```{r conf-mat-plot}
#| fig-height: 4
#| fig-width: 4.5
conf_mat(test_preds, truth = responded, estimate = .pred_class) |>
  autoplot(type = "heatmap")
```

::: {.callout-note title="From Confusion Matrix to Metrics"}
| Metric | Formula (informal) | Marketing question it answers |
|----|----|----|
| **Sensitivity** (recall) | TP / (TP + FN) | Of customers who *would* respond, how many did we catch? |
| **Specificity** | TN / (TN + FP) | Of customers who *wouldn't* respond, how many did we correctly skip? |
| **Precision (PPV)** | TP / (TP + FP) | Of customers we targeted, how many actually responded? |
| **Accuracy** | (TP + TN) / Total | Overall, how often is the model right? *(misleading with rare classes — see warning below)* |
:::

### Sensitivity (Recall)

::: {.callout-note title="Details"}
$$
\text{Sensitivity} = \frac{TP}{TP + FN}
$$

Where:

- $TP$ = true positives — customers who responded and were correctly predicted to respond
- $FN$ = false negatives — customers who responded but were incorrectly predicted not to respond
- $TP + FN$ = total number of actual responders
:::

### Specificity

::: {.callout-note title="Details"}
$$
\text{Specificity} = \frac{TN}{TN + FP}
$$

Where:

- $TN$ = true negatives — customers who did not respond and were correctly predicted not to respond
- $FP$ = false positives — customers who did not respond but were incorrectly predicted to respond
- $TN + FP$ = total number of actual non-responders
:::

### Precision (PPV)

::: {.callout-note title="Details"}
$$
\text{Precision} = \frac{TP}{TP + FP}
$$

Where:

- $TP$ = true positives — correctly predicted responders
- $FP$ = false positives — non-responders incorrectly predicted as responders
- $TP + FP$ = total number of customers predicted to respond
:::

### Accuracy

::: {.callout-note title="Details"}
$$
\text{Accuracy} = \frac{TP + TN}{TP + TN + FP + FN}
$$

Where:

- $TP$ = true positives
- $TN$ = true negatives
- $FP$ = false positives
- $FN$ = false negatives
- $TP + TN + FP + FN$ = total number of observations
:::

### F1 Score

::: {.callout-note title="Details"}
$$
F_1 = 2 \times \frac{\text{Precision} \times \text{Sensitivity}}{\text{Precision} + \text{Sensitivity}}
$$

Where:

- $\text{Precision} = \frac{TP}{TP + FP}$
- $\text{Sensitivity} = \frac{TP}{TP + FN}$
- $F_1$ is the harmonic mean of precision and sensitivity — useful when both matter equally and the classes are imbalanced
:::

```{r class-metrics}
class_metrics <- metric_set(accuracy, sens, spec, precision, f_meas)

test_preds |>
  class_metrics(truth = responded, estimate = .pred_class)
```

::: callout-warning
**Accuracy is dangerous with imbalanced classes.** Direct-mail response rates are often only 3–8%. A model that predicts "no" for *everyone* could still score 95%+ accuracy while being completely useless for targeting. Always check sensitivity/specificity alongside accuracy — this is exactly the kind of trap a stakeholder unfamiliar with the data could fall into.
:::

### ROC Curve and AUC

Sensitivity and specificity above were computed at a single classification threshold (0.5 by default). The **ROC curve** shows the sensitivity/specificity trade-off across *every possible* threshold, and **AUC** summarizes the whole curve in one number.

```{r roc-curve}
#| fig-height: 4.5
#| fig-width: 5
roc_data <- test_preds |>
  roc_curve(truth = responded, .pred_yes)

auc_val <- test_preds |>
  roc_auc(truth = responded, .pred_yes) |>
  pull(.estimate)
```

```{r roc-curve-plot}
autoplot(roc_data) +
  annotate(
    "text",
    x = 0.6,
    y = 0.2,
    label = paste0("AUC = ", round(auc_val, 3)),
    size = 5,
    color = "#2E5266",
    fontface = "bold"
  ) +
  labs(
    title = "ROC Curve — Direct-Mail Response Model",
    subtitle = "Closer to the top-left corner = better discrimination"
  ) +
  theme_minimal(base_size = 12)
```

::: callout-tip
**Rule of thumb.** AUC = 0.5 means the model is no better than a coin flip. AUC = 1.0 is a perfect classifier (rare in practice). For direct-mail targeting, AUC \> 0.65 is often usable; \> 0.75 is quite good.
:::

## Multiclass Classification Metrics

`loyalty_tier` (Bronze/Silver/Gold/Platinum) is a 4-level outcome. While we won't build a full multiclass model here, it's worth knowing how the binary metrics above generalize.

```{r multiclass-demo}
# Demonstration only: predict loyalty_tier from age + income as a toy multiclass model
multi_rec <- recipe(loyalty_tier ~ age + income, data = mail_train) |>
  step_impute_median(all_numeric_predictors()) |>
  step_normalize(all_numeric_predictors())

multi_spec <- multinom_reg() |> set_engine("nnet")

multi_wf <- workflow() |> add_recipe(multi_rec) |> add_model(multi_spec)
multi_fit <- fit(multi_wf, data = mail_train)

multi_preds <- augment(multi_fit, new_data = mail_test)

multi_preds |>
  metric_set(accuracy, sens)(truth = loyalty_tier, estimate = .pred_class)

multi_preds |>
  roc_auc(
    truth = loyalty_tier,
    .pred_Bronze,
    .pred_Silver,
    .pred_Gold,
    .pred_Platinum
  ) |>
  pull(.estimate)
```

::: {.callout-note title="How Binary Metrics Generalize to Multiclass"}
With more than two classes, `yardstick` computes a metric *per class* (treating each as "this class" vs. "all others"), then **averages** across classes. The default is **macro-averaging** — each class counts equally, regardless of how many observations it has. This matters for `loyalty_tier`: Platinum customers are rare, but macro-averaging keeps them from being drowned out by the much larger Bronze group.
:::

### Estimator Argument (Optional)

> Refer to Chapter 10
```{r multiclass-estimaor}
multi_preds |>
  metric_set(accuracy, sens)(
    truth = loyalty_tier,
    estimate = .pred_class,
    estimator = "macro"
  )

multi_preds |>
  metric_set(accuracy, sens)(
    truth = loyalty_tier,
    estimate = .pred_class,
    estimator = "macro_weighted"
  )

multi_preds |>
  metric_set(accuracy, sens)(
    truth = loyalty_tier,
    estimate = .pred_class,
    estimator = "micro"
  )

multi_preds |>
  roc_auc(
    truth = loyalty_tier,
    .pred_Bronze,
    .pred_Silver,
    .pred_Gold,
    .pred_Platinum,
    estimator = "macro_weighted"
  )
```

------------------------------------------------------------------------

# **Part 2** — Resampling for Evaluating Performance (TMWR Ch. 10)

The metrics above were all computed on a **single** test set. That gives us *a* number — but how much would that number change if we'd happened to split the data differently? Resampling answers this question.

## The Resubstitution Problem

What happens if we evaluate the model on the **same data it was trained on**?

```{r resubstitution}
train_preds <- augment(mail_fit, new_data = mail_train)

bind_rows(
  train_preds |>
    class_metrics(truth = responded, estimate = .pred_class) |>
    mutate(data = "training (resubstitution)"),
  test_preds |>
    class_metrics(truth = responded, estimate = .pred_class) |>
    mutate(data = "test (held out)")
) |>
  select(data, .metric, .estimate) |>
  pivot_wider(names_from = data, values_from = .estimate)
```

::: callout-important
**Resubstitution is optimistic.** The model has already "seen" the training data and partially memorized its noise, so performance measured there is inflated relative to how the model will do on genuinely new prospects. This gap is usually small for simple models like **regularized logistic regression**, but it can be large for flexible models (deep trees, boosted ensembles) — which is exactly why we need a principled way to estimate out-of-sample performance *without* permanently sacrificing data to a single test set.
:::

## Why Not Just Use the Test Set Repeatedly?

The test set should be touched **once**, at the very end, to report final performance. If we use it over and over while comparing models or tuning hyperparameters, we implicitly start fitting to it — defeating its purpose. Resampling lets us get reliable performance estimates **using only the training data**, keeping the test set untouched until final evaluation.

## Cross-Validation

The most common resampling scheme is **v-fold (k-fold) cross-validation**: split the training data into *v* roughly equal folds, train on *v − 1* of them, evaluate on the held-out fold, and rotate until every fold has served as the validation set exactly once.

```{r vfold}
set.seed(2024)
mail_folds <- vfold_cv(mail_train, v = 10, strata = responded)
mail_folds
```

```{r vfold-inspect}
# Look at one fold up close
mail_folds$splits[[1]]
```

::: {.callout-note title="What `vfold_cv()` Just Built"}
`mail_folds` is a tibble of 10 `rsplit` objects. Each one knows which rows of `mail_train` are the analysis set (≈ 90%, used for fitting) and which are the assessment set (≈ 10%, used for scoring) for that fold. `strata = responded` keeps the response rate roughly constant across folds — same logic as stratifying the original train/test split in Week 2.
:::

### Visualizing the Fold Structure

```{r fold-viz}
#| fig-height: 4
#| fig-width: 7
fold_viz <- map_dfr(seq_along(mail_folds$splits), function(i) {
  split <- mail_folds$splits[[i]]
  tibble(
    fold = i,
    row = 1:nrow(mail_train),
    role = if_else(
      row %in% split$in_id,
      "Analysis (train)",
      "Assessment (validate)"
    )
  )
})

ggplot(fold_viz, aes(x = row, y = factor(fold), fill = role)) +
  geom_tile() +
  scale_fill_manual(
    values = c(
      "Analysis (train)" = "#A9C0CC",
      "Assessment (validate)" = "#C0504D"
    )
  ) +
  labs(
    title = "10-Fold Cross-Validation Structure",
    subtitle = "Each row of the training data is held out exactly once",
    x = "Training set row index",
    y = "Fold",
    fill = NULL
  ) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom")
```

## Other Resampling Methods (Brief Tour)

```{r other-resampling}
# Repeated CV: run 10-fold CV five times with different random splits
repeated_folds <- vfold_cv(mail_train, v = 10, repeats = 5, strata = responded)
cat("Repeated CV total resamples:", nrow(repeated_folds), "\n")

# Bootstrap: sample WITH replacement, same size as training data
set.seed(2024)
boot_resamples <- bootstraps(mail_train, times = 25, strata = responded)
cat("Bootstrap resamples:", nrow(boot_resamples), "\n")

# Validation set: a single held-out chunk carved from the training data
val_set <- validation_split(mail_train, prop = 0.80, strata = responded)
val_set
```

::: {.callout-note title="Which Resampling Method When?"}
| Method | When to use it | Tradeoff |
|----|----|----|
| **V-fold CV** | Default choice for most marketing datasets | Good balance of bias and computation |
| **Repeated CV** | Smaller datasets where fold-to-fold variability is high | More stable estimates, *v* × *repeats* the compute |
| **Bootstrap** | Want a measure of estimate *uncertainty*, or very small data | Some observations never appear in assessment sets |
| **Validation set** | Very large data where CV is too slow | Only one estimate — less stable than CV |
| **Rolling origin** | Time-ordered data (e.g., monthly campaign cohorts) | Respects temporal order; no shuffling allowed |
:::

## Estimating Performance with `fit_resamples()`

This is where it all comes together: fit the workflow on each fold's analysis set, score it on the assessment set, and average the results.

```{r fit-resamples}
set.seed(2024)
cv_results <- fit_resamples(
  mail_wf,
  resamples = mail_folds,
  metrics = metric_set(accuracy, roc_auc, sens, spec),
  control = control_resamples(save_pred = TRUE)
)

cv_results
```

```{r collect-metrics}
collect_metrics(cv_results)
```

::: {.callout-important title="Comparing the Single Test Set vs. Cross-Validated Estimate"}
```{r compare-estimates}
bind_rows(
  test_preds |>
    metric_set(accuracy, roc_auc)(
      truth = responded,
      estimate = .pred_class,
      .pred_yes
    ) |>
    mutate(source = "Single test set"),
  collect_metrics(cv_results) |>
    filter(.metric %in% c("accuracy", "roc_auc")) |>
    select(.metric, .estimate = mean) |>
    mutate(source = "10-fold CV mean")
) |>
  select(source, .metric, .estimate) |>
  pivot_wider(names_from = source, values_from = .estimate)
```

The single test-set number is **one draw** from a distribution of possible performance estimates. The cross-validated mean averages over 10 different draws, giving a more stable — and more honest — picture of how the model is likely to perform on new prospects. The standard error reported by `collect_metrics()` tells us how much that estimate might wobble.
:::

```{r per-fold-metrics}
collect_metrics(cv_results, summarize = FALSE) |>
  filter(.metric == "roc_auc") |>
  ggplot(aes(x = id, y = .estimate)) +
  geom_col(fill = "#2E5266", alpha = 0.85) +
  geom_hline(
    aes(yintercept = mean(.estimate)),
    linetype = "dashed",
    color = "tomato"
  ) +
  labs(
    title = "ROC AUC by Fold",
    subtitle = "Dashed line = mean across all 10 folds",
    x = "Fold",
    y = "ROC AUC"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Parallel Processing (Conceptual Note)

```{r parallel-note, eval=FALSE}
# Resampling fits the same workflow many times — an embarrassingly parallel task.
# On a multi-core machine, register a parallel backend before fit_resamples():

# install.packages("doParallel")
library(doParallel)
cl <- makePSOCKcluster(parallel::detectCores() - 1)
registerDoParallel(cl)

cv_results <- fit_resamples(mail_wf, resamples = mail_folds)

stopCluster(cl)
```

::: callout-tip
We don't run this chunk live in class (it depends on your machine's core count), but know that `fit_resamples()`, `tune_grid()`, and friends all parallelize automatically once a backend is registered — useful once your resampling scheme + grid search gets large later in the course.
:::

## Saving Resampled Objects

```{r save-predictions}
# Because we set save_pred = TRUE above, we can pull out every held-out prediction
cv_preds <- collect_predictions(cv_results)
cv_preds |> select(id, .row, responded, .pred_class, .pred_yes) |> head()
```

```{r cv-roc}
#| fig-height: 4.5
#| fig-width: 5
cv_preds |>
  group_by(id) |>
  roc_curve(truth = responded, .pred_yes) |>
  ggplot(aes(x = 1 - specificity, y = sensitivity, color = id)) +
  geom_path(alpha = 0.6, linewidth = 0.8) +
  geom_abline(linetype = "dashed", color = "gray60") +
  labs(
    title = "ROC Curves Across All 10 Folds",
    subtitle = "Spread between lines = fold-to-fold variability",
    color = "Fold"
  ) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "none")
```

::: callout-note
**Why save predictions?** With `save_pred = TRUE`, we get every out-of-fold prediction back, which lets us build diagnostic plots like the multi-fold ROC curve above, inspect specific misclassified prospects, or build custom metrics — all without ever touching the test set.
:::

------------------------------------------------------------------------

# Exercises

## ✏️ Exercise 9.1 — Confusion Matrix and Threshold Tradeoff

**Part A — Reading the Confusion Matrix**

Run `conf_mat(test_preds, truth = responded, estimate = .pred_class)` and
use the output to answer:

1. How many customers actually responded ("yes") and were correctly
   predicted to respond? What is this cell called?
2. How many customers actually responded but were predicted "no"?
   What is this cell called, and what does it cost a marketer?
3. How many customers did not respond but were predicted "yes"?
   What is this cell called, and what does it cost a marketer?
4. In plain English, which type of error is more costly for a
   direct-mail campaign with a $5 mailing cost and $50 average order
   value — a false positive or a false negative? Explain your reasoning.

```{r ex9-1a, eval=FALSE}
# Your code here

```

**Part B — Threshold Tradeoff**

Using `test_preds`, compute `precision` and `sens` at the default 0.5
threshold. Now manually create a new `.pred_class` column using a threshold
of 0.3 instead (classify as "yes" if `.pred_yes > 0.3`). Recompute both
metrics. Which one increased, and why does lowering the threshold have
that effect?

```{r ex9-1b, eval=FALSE}
# Your code here

```

## ✏️ Exercise 9.2 — ROC/AUC Interpretation and Custom `metric_set()`

**Part A — Interpreting AUC**

The notebook computed `roc_auc` for the direct-mail response model.

1. Look up the AUC value from the `roc-curve` chunk. Is it above or
   below 0.65 (the "usable for targeting" threshold from the callout)?
2. In plain English, what does an AUC of that value mean? Complete
   this sentence: "If we randomly pick one customer who responded and
   one who did not, the model assigns a higher predicted probability
   to the responder \_\_\_\_% of the time."
3. The ROC curve plot shows the sensitivity/specificity tradeoff across
   all thresholds. At what point on the curve would you operate if your
   campaign budget only allows you to mail the top 10% of prospects?

```{r ex9-2a, eval=FALSE}
# Your code here

```

**Part B — Custom `metric_set()`**

Create a `metric_set()` containing `accuracy`, `roc_auc`, `sens`, `spec`,
and `f_meas`. Apply it to `test_preds`. If you had to report just **two**
of these five numbers to a VP of Marketing who is unfamiliar with
machine learning metrics, which would you choose and why?

```{r ex9-2b, eval=FALSE}
# Your code here

```
## ✏️ Exercise 9.3 — Regression Metric Sensitivity to Outliers

Add one synthetic "whale" customer to `reg_preds` with `order_value_next = 5000` and `.pred = 200` (a badly missed prediction). Recompute `rmse` and `mae`. Which metric moved more in percentage terms? What does this tell you about choosing RMSE vs. MAE for marketing data with occasional huge orders?

```{r ex9-3, eval=FALSE}
# Your code here

```

## ✏️ Exercise 9.4 — Multiclass Averaging

Re-run the multiclass `loyalty_tier` example using `estimator = "micro"`
instead of the default macro averaging for `sens`. Also run it with
`estimator = "macro_weighted"`. Compare all three numbers.

1. Why might micro-averaging look more favorable when one class (Bronze)
   is much larger than the others?
2. Which estimator would you choose if you wanted to ensure that
   **Platinum** customers — the rarest and most valuable tier — are
   not underrepresented in the metric? Explain your reasoning.
3. In a marketing context, which averaging method is most likely to give
   a misleadingly optimistic picture of model performance? Why?

```{r ex9-4, eval=FALSE}
# Your code here

```

## ✏️ Exercise 10.1 — Fold Count and Connecting Back to Part 1

**Part A — Change the Number of Folds**

Re-run `vfold_cv()` with `v = 5` instead of `v = 10`. Re-fit with
`fit_resamples()` and compare the mean `roc_auc` and its standard error
to the 10-fold result from the notebook. What happens to the standard
error as *v* decreases, and why?

```{r ex10-1a, eval=FALSE}
# Your code here

```

**Part B — Bridge to Part 1**

Now compare your 5-fold CV mean `roc_auc` to the single test-set
`roc_auc` you computed in Part 1 (Section 4 of the notebook).

1. Are the two numbers close or far apart? What does that tell you?
2. The single test-set number came from one particular 80/20 split.
   The CV number came from five different splits of the training data.
   Which is a more trustworthy estimate of how the model will perform
   on new prospects — and why?
3. The CV result comes with a standard error. What does that standard
   error represent, and why does the single test-set estimate not have
   one?

```{r ex10-1b, eval=FALSE}
# Retrieve the single test-set roc_auc from Part 1
test_preds |>
  roc_auc(truth = responded, .pred_yes)

# Your 5-fold CV result here

```

## ✏️ Exercise 10.2 — Bootstrap vs. Cross-Validation

Run `fit_resamples()` using `boot_resamples` (already created above) instead of `mail_folds`. Compare the mean `roc_auc` to the 10-fold CV result. Are they close? Which method gave a smaller standard error, and what about the bootstrap's sampling scheme might explain that?

```{r ex10-2, eval=FALSE}
# Your code here

```

## ✏️ Exercise 10.3 — Diagnose a High-Variance Fold

Looking at the "ROC AUC by Fold" plot above, identify the fold with the lowest AUC. Pull its assessment-set predictions from `cv_preds` and compute a confusion matrix just for that fold. Does anything about that fold's predictions look different from the others?

```{r ex10-3, eval=FALSE}
# Your code here

```

## ✏️ Exercise 10.4 — Resubstitution Gap and Model Flexibility

**Part A — Observe the Gap**

Refit `mail_wf` after changing `lr_spec` to a random forest:

```{r ex10-4a, eval=FALSE}
rf_spec <- rand_forest() |>
  set_engine("ranger") |>
  set_mode("classification")

rf_wf <- mail_wf |> update_model(rf_spec)

rf_fit <- fit(rf_wf, data = mail_train)
```

Compare resubstitution accuracy (on `mail_train`) to held-out accuracy
(on `mail_test`) for the random forest. Then do the same for the original
Lasso logistic regression from the notebook.

```{r ex10-4b, eval=FALSE}
# Random forest: resubstitution vs. held-out
rf_train_preds <- augment(rf_fit, new_data = mail_train)
rf_test_preds  <- augment(rf_fit, new_data = mail_test)

bind_rows(
  rf_train_preds |> accuracy(truth = responded, estimate = .pred_class) |>
    mutate(model = "Random Forest", data = "train (resubstitution)"),
  rf_test_preds  |> accuracy(truth = responded, estimate = .pred_class) |>
    mutate(model = "Random Forest", data = "test (held out)"),
  train_preds    |> accuracy(truth = responded, estimate = .pred_class) |>
    mutate(model = "Lasso LR",      data = "train (resubstitution)"),
  test_preds     |> accuracy(truth = responded, estimate = .pred_class) |>
    mutate(model = "Lasso LR",      data = "test (held out)")
) |>
  select(model, data, .estimate) |>
  pivot_wider(names_from = data, values_from = .estimate) |>
  mutate(gap = `train (resubstitution)` - `test (held out)`)
```

**Part B — Explain the Gap**

Answer the following in 3–5 sentences:

1. Is the resubstitution gap larger or smaller for the random forest
   compared to the Lasso logistic regression?
2. Why does model **flexibility** affect the size of the resubstitution
   gap? What is the random forest doing during training that the Lasso
   is not?
3. Given what you know about resubstitution, why is it dangerous to
   use training-set performance to select between a Lasso model and a
   random forest — and what should you use instead?

```{r ex10-4c, eval=FALSE}
# Use this space for any supporting calculations

```

------------------------------------------------------------------------

# Summary

| Concept | Function | Key Argument |
|----|----|----|
| Regression metrics | `rmse()`, `rsq()`, `mae()` | `truth`, `estimate` |
| Confusion matrix | `conf_mat()` | `truth`, `estimate` |
| Binary classification metrics | `sens()`, `spec()`, `precision()` | `truth`, `estimate` |
| Bundle multiple metrics | `metric_set()` | list of metric functions |
| ROC curve / AUC | `roc_curve()`, `roc_auc()` | `truth`, probability column |
| V-fold cross-validation | `vfold_cv()` | `v`, `strata` |
| Repeated cross-validation | `vfold_cv()` | `repeats` |
| Bootstrap resampling | `bootstraps()` | `times`, `strata` |
| Validation split | `validation_split()` | `prop`, `strata` |
| Fit + score across resamples | `fit_resamples()` | `resamples`, `metrics` |
| Pull averaged results | `collect_metrics()` | `summarize` |
| Pull raw out-of-fold predictions | `collect_predictions()` | requires `save_pred = TRUE` |

```{r session-info}
sessionInfo()
```
