---
title: "Week 3: Model Evaluation and Resampling"
subtitle: "IBM 6540 — Applied Machine Learning for Marketing"
author: "Jae Jung"
date: today
format:
  html:
    toc: true
    toc-depth: 4
    toc-expand: 1
    toc-location: right-body
    toc-title: "Contents"
    number-sections: true
    code-fold: show
    code-tools: true
    theme: cosmo
    highlight-style: github
    df-print: paged
    embed-resources: true
execute:
  warning: false
  message: false
  freeze: true
---

# Learning Objectives {.unnumbered}

By the end of this notebook you will be able to:

1.  Choose appropriate regression and classification metrics with `yardstick`
2.  Read and interpret a confusion matrix, sensitivity, specificity, and ROC/AUC
3.  Explain *why* evaluating a model on its own training data is overly optimistic (resubstitution)
4.  Build cross-validation folds with `vfold_cv()` and other resampling schemes with `rsample`
5.  Use `fit_resamples()` to get a trustworthy estimate of model performance
6.  Connect resampled performance back to the metrics from Section 1

> **Textbook reference:** *Tidy Modeling with R* (TMWR), Chapters 9 & 10 (<https://www.tmwr.org/performance>, <https://www.tmwr.org/resampling>)

------------------------------------------------------------------------

# Setup

```{r setup}
library(tidymodels) # umbrella: rsample, recipes, parsnip, workflows, yardstick
library(tidyverse)
library(gt) # pretty tables
library(patchwork) # combine plots

tidymodels_prefer() # resolve function-name conflicts
set.seed(2024)
```

------------------------------------------------------------------------

# The Marketing Dataset

We return to our synthetic **direct-mail** dataset from Week 2. Each row is one prospect; the outcome is whether they **responded** (bought).

```{r load-data}
# ── Synthetic direct-mail dataset (same generator as Week 2 / Week 7) ─────────
set.seed(123)
n <- 3000

mail_data <- tibble(
  customer_id = paste0("C", str_pad(1:n, 5, pad = "0")),
  age = round(rnorm(n, mean = 45, sd = 12)),
  income = round(rlnorm(n, meanlog = 10.8, sdlog = 0.6)), # right-skewed
  recency_days = round(rexp(n, rate = 1 / 60)), # days since last purchase
  freq_12mo = rpois(n, lambda = 3), # purchases in 12 months
  avg_order_amt = round(rlnorm(n, meanlog = 4.2, sdlog = 0.5), 2),
  channel = sample(
    c("email", "direct_mail", "digital"),
    n,
    replace = TRUE,
    prob = c(0.5, 0.3, 0.2)
  ),
  region = sample(
    c("West", "South", "Midwest", "Northeast"),
    n,
    replace = TRUE
  ),
  loyalty_tier = sample(
    c("Bronze", "Silver", "Gold", "Platinum"),
    n,
    replace = TRUE,
    prob = c(0.4, 0.3, 0.2, 0.1)
  ),
  responded = rbinom(
    n,
    1,
    prob = plogis(
      -3 +
        0.02 * (age - 45) +
        0.3 * log(income / 50000) +
        0.1 * freq_12mo -
        0.005 * recency_days
    )
  )
) |>
  mutate(
    income = if_else(runif(n) < 0.08, NA_real_, income),
    avg_order_amt = if_else(runif(n) < 0.05, NA_real_, avg_order_amt),
    responded = factor(responded, levels = c(1, 0), labels = c("yes", "no"))
  )
# introduce ~8 % missingness in income and avg_order_amt

glimpse(mail_data)
```

We also derive a **continuous** target — `order_value_next` — so we have a realistic stand-in for regression metrics in Section 1. Think of this as "expected next-order revenue," something a marketer might forecast for budget planning.

```{r derive-regression-target}
mail_data <- mail_data |>
  mutate(
    order_value_next = round(
      pmax(
        0,
        15 +
          0.0006 * coalesce(income, median(income, na.rm = TRUE)) +
          4 * freq_12mo -
          0.05 * recency_days +
          rnorm(n, 0, 20)
      ),
      2
    )
  )

mail_data |> select(customer_id, order_value_next) |> head()
```

::: callout-note
**Marketing context.** `responded` (yes/no) is our **classification** target — will this prospect respond to the next campaign? `order_value_next` is our **regression** target — how much will they spend on their next order? Both are common marketing prediction tasks, and TMWR Chapter 9 covers metrics for each.
:::

------------------------------------------------------------------------

# Train/Test Split and a Reference Model

Before we can evaluate anything, we need a fitted model. We reuse the same split-then-recipe workflow from Week 2.

```{r split}
set.seed(617)
mail_split <- initial_split(mail_data, prop = 0.80, strata = responded)
mail_train <- training(mail_split)
mail_test <- testing(mail_split)

cat("Training rows:", nrow(mail_train), "\n")
cat("Test rows    :", nrow(mail_test), "\n")
```

```{r recipe-model}
mail_rec <- recipe(
  responded ~ age +
    income +
    recency_days +
    freq_12mo +
    avg_order_amt +
    channel +
    region +
    loyalty_tier,
  data = mail_train
) |>
  step_impute_median(all_numeric_predictors()) |>
  step_log(income, avg_order_amt, recency_days, base = 10, offset = 1) |>
  step_normalize(all_numeric_predictors()) |>
  step_dummy(all_nominal_predictors()) |>
  step_zv(all_predictors())

lr_spec <- logistic_reg(penalty = 0.01, mixture = 1) |> # Lasso
  set_engine("glmnet") |>
  set_mode("classification")

mail_wf <- workflow() |>
  add_recipe(mail_rec) |>
  add_model(lr_spec)

mail_fit <- fit(mail_wf, data = mail_train)
```

```{r predict-test}
test_preds <- augment(mail_fit, new_data = mail_test)
test_preds |>
  select(customer_id, responded, .pred_class, .pred_yes, .pred_no) |>
  head()
```

------------------------------------------------------------------------

# Part 1 — Judging Model Effectiveness (TMWR Ch. 9)

A fitted model is only useful if we can say, in concrete numeric terms, *how good* its predictions are. `yardstick` is the tidymodels package for this — every metric function takes `truth` and an `estimate`/probability column and returns a tidy one-row tibble.

## Why Metrics, Not Just "It Fit"

::: callout-important
**There is no single "best" metric.** The right metric depends on the business question. For a churn model, missing a true churner (low **sensitivity**) might be far more costly than flagging a loyal customer by mistake (low **specificity**). Always pick metrics that match the marketing decision the model supports.
:::

## Regression Metrics

We don't have a regression *model* yet in this notebook, so we'll fit one quickly — predicting `order_value_next` from a few predictors — purely to demonstrate the metrics.

```{r reg-model}
reg_spec <- linear_reg() |>
  set_engine("lm")

reg_rec <- recipe(
  order_value_next ~ income + freq_12mo + recency_days,
  data = mail_train
) |>
  step_impute_median(all_numeric_predictors()) |>
  step_normalize(all_numeric_predictors())

reg_wf <- workflow() |> add_recipe(reg_rec) |> add_model(reg_spec)
reg_fit <- fit(reg_wf, data = mail_train)

reg_preds <- augment(reg_fit, new_data = mail_test)
reg_preds |> select(customer_id, order_value_next, .pred) |> head()
```

```{r reg-metrics}
reg_metrics <- metric_set(rmse, rsq, mae)

reg_preds |>
  reg_metrics(truth = order_value_next, estimate = .pred)
```

::: {.callout-note title="Reading Regression Metrics"}
- **RMSE** (root mean squared error): average prediction error, in the *original units* (dollars here). Penalizes large errors more heavily because errors are squared before averaging.
- **R² (rsq)**: proportion of variance in the outcome explained by the model. Ranges roughly 0–1; higher is better. Useful for communicating "how much of next-order value our model explains" to stakeholders.
- **MAE** (mean absolute error): average absolute error, less sensitive to outliers than RMSE. If a few extreme spenders are skewing RMSE, compare it against MAE.
:::

```{r reg-plot}
#| fig-height: 4.5
#| fig-width: 6
ggplot(reg_preds, aes(x = order_value_next, y = .pred)) +
  geom_point(alpha = 0.3, color = "#2E5266") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "tomato") +
  labs(
    title = "Predicted vs. Actual Next-Order Value",
    subtitle = "Dashed line = perfect prediction",
    x = "Actual order value ($)",
    y = "Predicted order value ($)"
  ) +
  theme_minimal(base_size = 12)
```

## Binary Classification Metrics

Back to our `responded` (yes/no) model. The starting point for classification metrics is the **confusion matrix**: a 2×2 table of predicted vs. actual class.

```{r conf-mat}
conf_mat(test_preds, truth = responded, estimate = .pred_class)
```

```{r conf-mat-plot}
#| fig-height: 4
#| fig-width: 4.5
conf_mat(test_preds, truth = responded, estimate = .pred_class) |>
  autoplot(type = "heatmap")
```

::: {.callout-note title="From Confusion Matrix to Metrics"}
| Metric | Formula (informal) | Marketing question it answers |
|----|----|----|
| **Sensitivity** (recall) | TP / (TP + FN) | Of customers who *would* respond, how many did we catch? |
| **Specificity** | TN / (TN + FP) | Of customers who *wouldn't* respond, how many did we correctly skip? |
| **Precision (PPV)** | TP / (TP + FP) | Of customers we targeted, how many actually responded? |
| **Accuracy** | (TP + TN) / Total | Overall, how often is the model right? *(misleading with rare classes — see warning below)* |
:::

```{r class-metrics}
class_metrics <- metric_set(accuracy, sens, spec, precision, f_meas)

test_preds |>
  class_metrics(truth = responded, estimate = .pred_class)
```

::: callout-warning
**Accuracy is dangerous with imbalanced classes.** Direct-mail response rates are often only 3–8%. A model that predicts "no" for *everyone* could still score 95%+ accuracy while being completely useless for targeting. Always check sensitivity/specificity alongside accuracy — this is exactly the kind of trap a stakeholder unfamiliar with the data could fall into.
:::

### ROC Curve and AUC

Sensitivity and specificity above were computed at a single classification threshold (0.5 by default). The **ROC curve** shows the sensitivity/specificity trade-off across *every possible* threshold, and **AUC** summarizes the whole curve in one number.

```{r roc-curve}
#| fig-height: 4.5
#| fig-width: 5
roc_data <- test_preds |>
  roc_curve(truth = responded, .pred_yes)

auc_val <- test_preds |>
  roc_auc(truth = responded, .pred_yes) |>
  pull(.estimate)

autoplot(roc_data) +
  annotate(
    "text",
    x = 0.6,
    y = 0.2,
    label = paste0("AUC = ", round(auc_val, 3)),
    size = 5,
    color = "#2E5266",
    fontface = "bold"
  ) +
  labs(
    title = "ROC Curve — Direct-Mail Response Model",
    subtitle = "Closer to the top-left corner = better discrimination"
  ) +
  theme_minimal(base_size = 12)
```

::: callout-tip
**Rule of thumb.** AUC = 0.5 means the model is no better than a coin flip. AUC = 1.0 is a perfect classifier (rare in practice). For direct-mail targeting, AUC \> 0.65 is often usable; \> 0.75 is quite good.
:::

## Multiclass Classification Metrics

`loyalty_tier` (Bronze/Silver/Gold/Platinum) is a 4-level outcome. While we won't build a full multiclass model here, it's worth knowing how the binary metrics above generalize.

```{r multiclass-demo}
# Demonstration only: predict loyalty_tier from age + income as a toy multiclass model
multi_rec <- recipe(loyalty_tier ~ age + income, data = mail_train) |>
  step_impute_median(all_numeric_predictors()) |>
  step_normalize(all_numeric_predictors())

multi_spec <- multinom_reg() |> set_engine("nnet")

multi_wf <- workflow() |> add_recipe(multi_rec) |> add_model(multi_spec)
multi_fit <- fit(multi_wf, data = mail_train)

multi_preds <- augment(multi_fit, new_data = mail_test)

multi_preds |>
  metric_set(accuracy, sens)(truth = loyalty_tier, estimate = .pred_class)
```

::: {.callout-note title="How Binary Metrics Generalize to Multiclass"}
With more than two classes, `yardstick` computes a metric *per class* (treating each as "this class" vs. "all others"), then **averages** across classes. The default is **macro-averaging** — each class counts equally, regardless of how many observations it has. This matters for `loyalty_tier`: Platinum customers are rare, but macro-averaging keeps them from being drowned out by the much larger Bronze group.
:::

------------------------------------------------------------------------

# Part 2 — Resampling for Evaluating Performance (TMWR Ch. 10)

The metrics above were all computed on a **single** test set. That gives us *a* number — but how much would that number change if we'd happened to split the data differently? Resampling answers this question.

## The Resubstitution Problem

What happens if we evaluate the model on the **same data it was trained on**?

```{r resubstitution}
train_preds <- augment(mail_fit, new_data = mail_train)

bind_rows(
  train_preds |>
    class_metrics(truth = responded, estimate = .pred_class) |>
    mutate(data = "training (resubstitution)"),
  test_preds |>
    class_metrics(truth = responded, estimate = .pred_class) |>
    mutate(data = "test (held out)")
) |>
  select(data, .metric, .estimate) |>
  pivot_wider(names_from = data, values_from = .estimate)
```

::: callout-important
**Resubstitution is optimistic.** The model has already "seen" the training data and partially memorized its noise, so performance measured there is inflated relative to how the model will do on genuinely new prospects. This gap is usually small for simple models like regularized logistic regression, but it can be large for flexible models (deep trees, boosted ensembles) — which is exactly why we need a principled way to estimate out-of-sample performance *without* permanently sacrificing data to a single test set.
:::

## Why Not Just Use the Test Set Repeatedly?

The test set should be touched **once**, at the very end, to report final performance. If we use it over and over while comparing models or tuning hyperparameters, we implicitly start fitting to it — defeating its purpose. Resampling lets us get reliable performance estimates **using only the training data**, keeping the test set untouched until final evaluation.

## Cross-Validation

The most common resampling scheme is **v-fold (k-fold) cross-validation**: split the training data into *v* roughly equal folds, train on *v − 1* of them, evaluate on the held-out fold, and rotate until every fold has served as the validation set exactly once.

```{r vfold}
set.seed(2024)
mail_folds <- vfold_cv(mail_train, v = 10, strata = responded)
mail_folds
```

```{r vfold-inspect}
# Look at one fold up close
mail_folds$splits[[1]]
```

::: {.callout-note title="What `vfold_cv()` Just Built"}
`mail_folds` is a tibble of 10 `rsplit` objects. Each one knows which rows of `mail_train` are the analysis set (≈ 90%, used for fitting) and which are the assessment set (≈ 10%, used for scoring) for that fold. `strata = responded` keeps the response rate roughly constant across folds — same logic as stratifying the original train/test split in Week 2.
:::

### Visualizing the Fold Structure

```{r fold-viz}
#| fig-height: 4
#| fig-width: 7
fold_viz <- map_dfr(seq_along(mail_folds$splits), function(i) {
  split <- mail_folds$splits[[i]]
  tibble(
    fold = i,
    row = 1:nrow(mail_train),
    role = if_else(
      row %in% split$in_id,
      "Analysis (train)",
      "Assessment (validate)"
    )
  )
})

ggplot(fold_viz, aes(x = row, y = factor(fold), fill = role)) +
  geom_tile() +
  scale_fill_manual(
    values = c(
      "Analysis (train)" = "#A9C0CC",
      "Assessment (validate)" = "#C0504D"
    )
  ) +
  labs(
    title = "10-Fold Cross-Validation Structure",
    subtitle = "Each row of the training data is held out exactly once",
    x = "Training set row index",
    y = "Fold",
    fill = NULL
  ) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom")
```

## Other Resampling Methods (Brief Tour)

```{r other-resampling}
# Repeated CV: run 10-fold CV five times with different random splits
repeated_folds <- vfold_cv(mail_train, v = 10, repeats = 5, strata = responded)
cat("Repeated CV total resamples:", nrow(repeated_folds), "\n")

# Bootstrap: sample WITH replacement, same size as training data
set.seed(2024)
boot_resamples <- bootstraps(mail_train, times = 25, strata = responded)
cat("Bootstrap resamples:", nrow(boot_resamples), "\n")

# Validation set: a single held-out chunk carved from the training data
val_set <- validation_split(mail_train, prop = 0.80, strata = responded)
val_set
```

::: {.callout-note title="Which Resampling Method When?"}
| Method | When to use it | Tradeoff |
|----|----|----|
| **V-fold CV** | Default choice for most marketing datasets | Good balance of bias and computation |
| **Repeated CV** | Smaller datasets where fold-to-fold variability is high | More stable estimates, *v* × *repeats* the compute |
| **Bootstrap** | Want a measure of estimate *uncertainty*, or very small data | Some observations never appear in assessment sets |
| **Validation set** | Very large data where CV is too slow | Only one estimate — less stable than CV |
| **Rolling origin** | Time-ordered data (e.g., monthly campaign cohorts) | Respects temporal order; no shuffling allowed |
:::

## Estimating Performance with `fit_resamples()`

This is where it all comes together: fit the workflow on each fold's analysis set, score it on the assessment set, and average the results.

```{r fit-resamples}
set.seed(2024)
cv_results <- fit_resamples(
  mail_wf,
  resamples = mail_folds,
  metrics = metric_set(accuracy, roc_auc, sens, spec),
  control = control_resamples(save_pred = TRUE)
)

cv_results
```

```{r collect-metrics}
collect_metrics(cv_results)
```

::: {.callout-important title="Comparing the Single Test Set vs. Cross-Validated Estimate"}
```{r compare-estimates}
bind_rows(
  test_preds |>
    metric_set(accuracy, roc_auc)(
      truth = responded,
      estimate = .pred_class,
      .pred_yes
    ) |>
    mutate(source = "Single test set"),
  collect_metrics(cv_results) |>
    filter(.metric %in% c("accuracy", "roc_auc")) |>
    select(.metric, .estimate = mean) |>
    mutate(source = "10-fold CV mean")
) |>
  select(source, .metric, .estimate) |>
  pivot_wider(names_from = source, values_from = .estimate)
```

The single test-set number is **one draw** from a distribution of possible performance estimates. The cross-validated mean averages over 10 different draws, giving a more stable — and more honest — picture of how the model is likely to perform on new prospects. The standard error reported by `collect_metrics()` tells us how much that estimate might wobble.
:::

```{r per-fold-metrics}
collect_metrics(cv_results, summarize = FALSE) |>
  filter(.metric == "roc_auc") |>
  ggplot(aes(x = id, y = .estimate)) +
  geom_col(fill = "#2E5266", alpha = 0.85) +
  geom_hline(
    aes(yintercept = mean(.estimate)),
    linetype = "dashed",
    color = "tomato"
  ) +
  labs(
    title = "ROC AUC by Fold",
    subtitle = "Dashed line = mean across all 10 folds",
    x = "Fold",
    y = "ROC AUC"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Parallel Processing (Conceptual Note)

```{r parallel-note, eval=FALSE}
# Resampling fits the same workflow many times — an embarrassingly parallel task.
# On a multi-core machine, register a parallel backend before fit_resamples():

library(doParallel)
cl <- makePSOCKcluster(parallel::detectCores() - 1)
registerDoParallel(cl)

cv_results <- fit_resamples(mail_wf, resamples = mail_folds)

stopCluster(cl)
```

::: callout-tip
We don't run this chunk live in class (it depends on your machine's core count), but know that `fit_resamples()`, `tune_grid()`, and friends all parallelize automatically once a backend is registered — useful once your resampling scheme + grid search gets large later in the course.
:::

## Saving Resampled Objects

```{r save-predictions}
# Because we set save_pred = TRUE above, we can pull out every held-out prediction
cv_preds <- collect_predictions(cv_results)
cv_preds |> select(id, .row, responded, .pred_class, .pred_yes) |> head()
```

```{r cv-roc}
#| fig-height: 4.5
#| fig-width: 5
cv_preds |>
  group_by(id) |>
  roc_curve(truth = responded, .pred_yes) |>
  ggplot(aes(x = 1 - specificity, y = sensitivity, color = id)) +
  geom_path(alpha = 0.6, linewidth = 0.8) +
  geom_abline(linetype = "dashed", color = "gray60") +
  labs(
    title = "ROC Curves Across All 10 Folds",
    subtitle = "Spread between lines = fold-to-fold variability",
    color = "Fold"
  ) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "none")
```

::: callout-note
**Why save predictions?** With `save_pred = TRUE`, we get every out-of-fold prediction back, which lets us build diagnostic plots like the multi-fold ROC curve above, inspect specific misclassified prospects, or build custom metrics — all without ever touching the test set.
:::

------------------------------------------------------------------------

# Exercises

## ✏️ Exercise 9.1 — Precision vs. Sensitivity Tradeoff

Using `test_preds`, compute `precision` and `sens` at the default 0.5 threshold. Now manually create a new `.pred_class` column using a threshold of 0.3 instead (classify as "yes" if `.pred_yes > 0.3`). Recompute both metrics. Which one increased, and why does lowering the threshold have that effect?

```{r ex9-1, eval=FALSE}
# Your code here

```

## ✏️ Exercise 9.2 — Build a Custom `metric_set()`

Create a `metric_set()` containing `accuracy`, `roc_auc`, `sens`, `spec`, and `f_meas`. Apply it to `test_preds`. If you had to report just **two** of these five numbers to a VP of Marketing, which would you choose and why?

```{r ex9-2, eval=FALSE}
# Your code here

```

## ✏️ Exercise 9.3 — Regression Metric Sensitivity to Outliers

Add one synthetic "whale" customer to `reg_preds` with `order_value_next = 5000` and `.pred = 200` (a badly missed prediction). Recompute `rmse` and `mae`. Which metric moved more in percentage terms? What does this tell you about choosing RMSE vs. MAE for marketing data with occasional huge orders?

```{r ex9-3, eval=FALSE}
# Your code here

```

## ✏️ Exercise 9.4 — Multiclass Averaging

Re-run the multiclass `loyalty_tier` example using `estimator = "micro"` instead of the default macro averaging for `sens`. Compare the two numbers. Why might micro-averaging look more favorable when one class (Bronze) is much larger than the others?

```{r ex9-4, eval=FALSE}
# Your code here

```

## ✏️ Exercise 10.1 — Change the Number of Folds

Re-run `vfold_cv()` with `v = 5` instead of `v = 10`. Re-fit with `fit_resamples()` and compare the mean `roc_auc` and its standard error to the 10-fold result. What happens to the standard error as *v* decreases, and why?

```{r ex10-1, eval=FALSE}
# Your code here

```

## ✏️ Exercise 10.2 — Bootstrap vs. Cross-Validation

Run `fit_resamples()` using `boot_resamples` (already created above) instead of `mail_folds`. Compare the mean `roc_auc` to the 10-fold CV result. Are they close? Which method gave a smaller standard error, and what about the bootstrap's sampling scheme might explain that?

```{r ex10-2, eval=FALSE}
# Your code here

```

## ✏️ Exercise 10.3 — Diagnose a High-Variance Fold

Looking at the "ROC AUC by Fold" plot above, identify the fold with the lowest AUC. Pull its assessment-set predictions from `cv_preds` and compute a confusion matrix just for that fold. Does anything about that fold's predictions look different from the others?

```{r ex10-3, eval=FALSE}
# Your code here

```

## ✏️ Exercise 10.4 — Resubstitution Gap with a More Flexible Model

Refit `mail_wf` after changing `lr_spec` to a random forest (`rand_forest() |> set_engine("ranger") |> set_mode("classification")`). Compare resubstitution accuracy (on `mail_train`) to held-out accuracy (on `mail_test`). Is the gap larger or smaller than it was for the Lasso logistic regression? Why might that be?

```{r ex10-4, eval=FALSE}
# Your code here

```

------------------------------------------------------------------------

# Summary

| Concept | Function | Key Argument |
|----|----|----|
| Regression metrics | `rmse()`, `rsq()`, `mae()` | `truth`, `estimate` |
| Confusion matrix | `conf_mat()` | `truth`, `estimate` |
| Binary classification metrics | `sens()`, `spec()`, `precision()` | `truth`, `estimate` |
| Bundle multiple metrics | `metric_set()` | list of metric functions |
| ROC curve / AUC | `roc_curve()`, `roc_auc()` | `truth`, probability column |
| V-fold cross-validation | `vfold_cv()` | `v`, `strata` |
| Repeated cross-validation | `vfold_cv()` | `repeats` |
| Bootstrap resampling | `bootstraps()` | `times`, `strata` |
| Validation split | `validation_split()` | `prop`, `strata` |
| Fit + score across resamples | `fit_resamples()` | `resamples`, `metrics` |
| Pull averaged results | `collect_metrics()` | `summarize` |
| Pull raw out-of-fold predictions | `collect_predictions()` | requires `save_pred = TRUE` |

```{r session-info}
sessionInfo()
```
